TOI based ProVisioNet

### 2021-11-16 01_studies/01_Laborstudie ProVisioNET/R script/reli/ProVisioNet_ET_reli_01_01_TOI-based_data.Rmd
Coding data metrics + SRI + SJT

```{r}
if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
if (!require(papaja)) install.packages("papaja"); library(papaja)
if (!require(psych)) install.packages('psych'); library(psych) # stats
if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
if (!require(DescTools)) install.packages('DescTools'); library(DescTools) # cohens kappa
if (!require(irr)) install.packages('irr'); library(irr) # Various Coefficients of Interrater Reliability and Agreement
if (!require(readxl)) install.packages('readxl'); library(readxl) # read in excel files

```

@@

ggplot(data = filter(df_cappa_dur,
                     TOI != "Lesson"),
       mapping = aes(x = Duration_of_interval_AP,
                     y = Duration_of_interval_MK
                     )
       ) +
  geom_point(size = 2) +
  geom_abline(intercept = 0,
              slope = 1,
              color = "red",
              linetype = 3
              ) +
  labs(x = "Duration coded by AP",
       y = "Duration coded by MK",
       title = "Inter-coder reliability"
       ) +
  theme_minimal()
```

@@

ggplot(data = filter(df_cappa_start,
                     TOI != "Lesson"),
       mapping = aes(x = Start_of_interval_AP,
                     y = Start_of_interval_MK
                     )
       ) +
  geom_point(size = 2) +
  geom_abline(intercept = 0,
              slope = 1,
              color = "red",
              linetype = 3
              ) +
  labs(x = "Start coded by AP",
       y = "Start coded by MK",
       title = "Inter-coder reliability"
       ) +
  theme_minimal()
```

>>>>

```{r}
library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl)
```

@@

ggplot(data = filter(df_cappa_dur,
                     TOI != "Lesson"),
       mapping = aes(x = Duration_of_interval_AP,
                     y = Duration_of_interval_MK
                     )
       ) +
  geom_point(size = 2) +
  geom_text(mapping = aes(label = TOI)
            ) +
  geom_abline(intercept = 0,
              slope = 1,
              color = "red",
              linetype = 3
              ) +
  labs(x = "Duration coded by AP",
       y = "Duration coded by MK",
       title = "Inter-coder reliability"
       ) +
  theme_minimal()
```

@@

ggplot(data = filter(df_cappa_start,
                     TOI != "Lesson"),
       mapping = aes(x = Start_of_interval_AP,
                     y = Start_of_interval_MK
                     )
       ) +
  geom_point(size = 2) +
  geom_text(mapping = aes(label = TOI)
            ) +
  geom_abline(intercept = 0,
              slope = 1,
              color = "red",
              linetype = 3
              ) +
  labs(x = "Start coded by AP",
       y = "Start coded by MK",
       title = "Inter-coder reliability"
       ) +
  theme_minimal()
```
